\documentclass[margin]{res3}

\usepackage{url}

\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\oddsidemargin -.3in \evensidemargin -.4in \textwidth=5.6in
\topmargin=0.2in \textheight=9.3in \itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0.03in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0.02in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

%\vspace{10pt}

\hspace{1.8in}{\LARGE \bf Yi \hspace{5pt}Yang}

% \vspace{8pt}

%\begin{tabular}{@{}p{1.65in}p{2.15in}p{2in}}
%  \hspace{-1in}Contact Info & Baidu USA LLC   & Mobile:   (+1) 650-630-9378 \\
%              \hspace{-1in} & One Microsoft Way &  Email:  nikai97@gmail.com \\
%              \hspace{-1in} & Redmond, WA 98052  & http://www.kaini.org \\
%\end{tabular}
\vspace{-10pt}
\hspace{-0.4in}\makebox[\linewidth]{\rule{6.8in}{1pt}} 
\vspace{-10pt}

\begin{resume}

% Contact Information
\section{\sc Contact}
\begin{tabular}{@{}p{4.15in}p{2.15in}}
  Mobile: (+1) 949-272-6066, (+44) 7384-871096 & Google DeepMind\\
  Email: yiya@google.com, yangyi02@gmail.com & 6 Pancras Square\\
  Webpage: \url{http://yangyi02.github.io} & Kings Cross, London, N1C 4AG\\
\end{tabular}


% Research Interests
% \vspace{-15pt}
\section{\sc Interests}
Deep Learning, Computer Vision, Machine Learning, Reinforcement Learning
% \begin{list2}
% \item Object Detection, Image Segmentation, Articulated Pose Estimation
% \vspace{-14pt}
% \item Deep Learning, Reinforcement Learning
% \vspace{-2pt}
% \item Image Captioning, Image Question Answering
% \end{list2}


% Education
\section{\sc Education}
{\bf University of California Irvine} \hfill{2008 - 2013}
\begin{list2}
\item Ph.D. in Computer Science \hfill{GPA: 3.95/4.0}
\vspace{-2pt}
\item Advisor: Prof. Deva Ramanan, co-advisor: Prof. Charless Fowlkes 
\end{list2}
\vspace{-2pt}\vspace{-2pt}\vspace{-2pt}

{\bf Hong Kong University of Science \& Technology} \hfill {2006 - 2008}
\begin{list2}
\item M.Phil. in Industrial Engineering and Logistic Management \hfill {GPA: 3.5/4.0}
\vspace{-2pt}
\item Advisor: Prof. Jeff Hong 
\end{list2}
\vspace{-2pt}\vspace{-2pt}\vspace{-2pt}

{\bf Tsinghua University} \hfill {2002 - 2006}
\begin{list2}
\item B.S. in Automation \hfill {GPA: 3.8/4.0}
\vspace{-2pt}
\item Top 10\% with Excellent Graduation Award 
\end{list2}


% Research Experience
\section{\sc Experience}

\begin{list1}

\item[] {\bf Google DeepMind, London} \hfill {11/2018 - Present}
\vspace{-2pt}
\item[] Research Scientist \hfill {London, UK}

\begin{list2}
\item Multilingual lip sync from audio.
\vspace{-2pt}
\item Self-supervised 3D optical flow.
\end{list2}
\vspace{5pt}


\item[] {\bf Baidu Research, Silicon Valley} \hfill {10/2013 - 10/2018}
\vspace{-2pt}
\item[] Research Scientist, Institute of Deep Learning \hfill {Sunnyvale, CA}

\begin{list2}
\item Occlusion aware unsupervised learning of optical flow.
\vspace{-2pt}
\item Dynamic computational time for visual attention.
\vspace{-2pt}
\item Semantic image segmentation with deep convolutional neural networks.
\vspace{-2pt}
\item Object detection with deep convolutional neural networks.
\vspace{-2pt}
\item Image captioning and question answering with multimodal recurrent neural networks.
\vspace{-2pt}
\item Learning from massive noisy labeled data for visual classification.
\vspace{-2pt}
\item Feedback neural networks for object detection and fine-grained recognition.
\end{list2}
\vspace{5pt}


\item[] {\bf Google, Mountain View} \hfill {06/2012 - 09/2012}
\vspace{-2pt}
\item[] Software Engineer Intern, Google Shopping Team \hfill {Mountain View, CA}
\vspace{-2pt}
\item[] Mentor: Emilio Antunez, co-mentor: Tianli Yu 

\begin{list2}
\item Large scale human pose estimation for visual fashion clothing retrieval.	
%\vspace{-2pt}
%\item Developed a large scale parallel pose estimation and evaluation system using Google’s MapReduce infrastructure.
%\vspace{-2pt}
%\item Achieved state-of-the-art pose estimation accuracy, especially on the most difficult arm localization task, outperforming previous best algorithms by 20\% in 50K images.
%\vspace{-2pt}
%\item Methods are applied for automatic clothing segmentation and fashion image retrieval in the Google Shopping recommendation system.
\end{list2}
\vspace{5pt}


\item[] {\bf Microsoft Research, Silicon Valley} \hfill {06/2011 - 09/2011}
\vspace{-2pt}
\item[] Research Intern, Interactive Visual Media Lab \hfill{Mountain View, CA}
\vspace{-2pt}
\item[] Mentor: Simon Baker, co-mentor: Anitha Kannan

\begin{list2}
\item Proxemics recognition for multiple people interactions in personal photo albums.
%\vspace{-2pt}
%\item Studied a completely novel computer vision problem - proxemics detection.
%\vspace{-2pt}
%\item Developed a pictorial structure model and achieved state-of-the-art proxemics detection performance 
%\vspace{-2pt}
%\item Methods are applied for recognizing multiple people interactions in the Microsoft AutoCaption mobile app.
\end{list2}
\vspace{5pt}


\item[] {\bf University of California Irvine} \hfill {09/2008 - 08/2013}
\vspace{-2pt}
\item[] Research Assistant, Computer Vision Lab \hfill {Irvine, CA}
\vspace{-2pt}
\item[] Advisor: Prof. Deva Ramanan, co-advisor: Prof. Charless Fowlkes

\begin{list2}
\item Human detection and parsing under occlusion and truncation.
\vspace{-2pt}
\item Articulated pose estimation with flexible mixtures-of-parts.
\vspace{-2pt}
\item Layered object detection for multi-class image segmentation.
\end{list2}
\vspace{5pt}


% \item[] {\bf ENW Electronics Ltd., Hong Kong} \hfill {03/2007 - 03/2008}
% \vspace{-2pt}
% \item[] Manufacturing Consultant Assistant, Worked with Prof. Jeff Hong \hfill {Hong Kong}
% \vspace{-2pt}
 
% \begin{list2}
% \item Improving manufacturing efficiency and production management at ENW Electronics Ltd.
% \vspace{-2pt}
% \item Investigated production flow and manufacturing management situations in ENW Ltd.
% \vspace{-2pt}
% \item Provided implementation suggestions for improving production efficiency and management quality for company managers every week.
% \vspace{-2pt}
% \item Developed an automatic scheduling software package for ENW production management.
% \vspace{5pt}
% \end{list2}

\end{list1}

% Publications
\section{\sc Selected Publications}
\begin{list1}

\item[] 20. Xiangyun Zhao, Yi Yang, Feng Zhou, Xiao Tan, Yuchen Yuan, Yingze Bao, Ying Wu,
``Recognizing Part Attributes with Insufficient Data'',
  in \textit{ICCV 2019}

\item[] 19. Yang Wang, Peng Wang, Zhenheng Yang, Chenxu Luo, Yi Yang, Wei Xu, 
``UnOS: Unified Unsupervised Optical-flow and Stereo-depth Estimation by Watching Videos'',
in \textit{CVPR 2019}.

\item[] 18. Yang Wang, Yi Yang, Zhenheng Yang, Liang Zhao, Peng Wang, Wei Xu,
``Occlusion Aware Unsupervised Learning of Optical Flow'',
in \textit{CVPR 2018}.

\item[] 17. Chunshui Cao, Xianming Liu, Yi Yang, et al.,
``Feedback Convolutional Neural Network for Visual Localization and Segmentation'',
in \textit{PAMI 2018}.

\item[] 16. James Supancic, Gregory Rogez, Yi Yang, Jamie Shotton, Deva Ramanan,
``Depth-based Hand Pose Estimation: Data, Methods, and Challenges'',
in \textit{IJCV 2018}.

\item[] 15. Liang-Chieh Chen, Yi Yang, Jiang Wang, Wei Xu, and Alan L. Yuille, 
``Attention to Scale: Scale-aware Semantic Image Segmentation",
in \textit{CVPR 2016}.

\item[] 14. Jiang Wang, Yi Yang, Junhua Mao, Zhiheng Huang, Chang Huang, Wei Xu, 
``CNN-RNN: A Unified Framework for Multi-label Image Classification",
in \textit{CVPR 2016}. (Oral; Acceptance Rate: 3.9\%)

\item[] 13. Haonan Yu, Jiang Wang, Zhiheng Huang, Yi Yang, Wei Xu, 
``Video Paragraph Captioning Using Hierarchical Recurrent Neural Networks",
in \textit{CVPR 2016}. (Oral; Acceptance Rate: 3.9\%)

\item[] 12. Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Zhiheng Huang, Alan Yuille,
``Learning like a Child: Fast Novel Visual Concept Learning from Sentence Descriptions of Images",
in \textit{ICCV 2015}.
% in \textit{Proceedings of IEEE Computer Society Conference on Computer Vision and Pattern Recognition (ICCV)}, Boston, Chile, 2015

\item[] 11. James Supan\v{c}i\v{c}, Gregory Rogez, Yi Yang, Jamie Shotton, Deva Ramanan, 
``Depth-based hand pose estimation: data, methods, and challenges",
in \textit{ICCV 2015}.

\item[] 10. Chunshui Cao, Xianming Liu, Yi Yang, et al.,
``Look and Think Twice: Capturing Top-Down Visual Attention with Feedback Convolutional Neural Networks",
in \textit{ICCV 2015}. 

\item[] 9. Tong Xiao, Tian Xia, Yi Yang, Chang Huang, Xiaogang Wang,
``Learning from Massive Noisy Labeled Data for Image Classification",
in \textit{CVPR 2015}.
% in \textit{Proceedings of IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR)}, Boston, MA, 2015

\item[] 8. Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Zhiheng Huang and Alan Yuille,
``Deep Captioning with Multimodal Recurrent Neural Networks",
in \textit{ICLR 2015}.
% in \textit{International Conference in Learning Representations (ICLR)}, San Diego, 2015

\item[] 7. Golnaz Ghiasi, Yi Yang, Charless Fowlkes and Deva Ramanan, 
``Parsing Occluded People", 
in \textit{CVPR 2014}.
% in \textit{Proceedings of IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR)}, Columbus, OH, 2014.

\item[] 6. Yi Yang and Deva Ramanan, 
``Articulated Human Detection with Flexible Mixtures-of-Parts", 
in \textit{PAMI 2013}.
% in \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence (PAMI)}, 2013. 

\item[] 5. Yi Yang, Simon Baker, Anitha Kannan and Deva Ramanan, 
``Recognizing Proxemics in Personal Photos", 
in \textit{CVPR 2012}.
% in \textit{Proceedings of IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR)}, Providence, RI, 2012

\item[] 4. Yi Yang, Sam Hallman, Deva Ramanan and Charless Fowlkes, 
``Layered Object Models for Image Segmentation", 
in \textit{PAMI 2012}.
% in \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence (PAMI)}, 2012. 

\item[] 3. Yi Yang and Deva Ramanan, 
``Articulated Pose Estimation with Flexible Mixtures-of-Parts", 
in \textit{CVPR 2011}. (Oral; Acceptance Rate: 3.5\%)
% in \textit{Proceedings of IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR)}, Colorado Spring, CO, 2011 (Oral; Acceptance Rate: 3.5\%)

\item[] 2. Jeff Hong, Yi Yang, and Liwei Zhang, 
``Sequential Convex Approximations to Joint Chance Constrained Programs: a Monte Carlo Approach,"
% in \textit{Operations Research (OR), 2011}.
in \textit{OR 2011}.

\item[] 1. Yi Yang, Sam Hallman, Deva Ramanan and Charless Fowlkes,
``Layered Object Detection for Multi-Class Segmentation",
in \textit{CVPR 2010}. (Oral; Acceptance Rate: 4.5\%)
% in \textit{Proceedings of IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR)}, San Francisco, CA, 2010. (Oral; Acceptance Rate: 4.5\%)

\end{list1}


% Honors and Awards
\section{\sc Activities and Awards}

\begin{list1}
\item[] Baidu Top Performer Awards ($\ll$ 1\%) \hfill{2016}

\item[] Conference Review: NIPS, CVPR, ICCV, ECCV, etc. \hfill{2012 - Present}

\item[] Journal Review: PAMI, IJCV, etc. \hfill{2012 - 2015}

\item[] Research Fellowship, UC Irvine \hfill{2011 - 2013}

\item[]	ICS Fellowship Award, UC Irvine \hfill{2008 - 2011}

\item[]	Research Fellowship, HKUST \hfill{2006 - 2008}

\item[]	Excellent Graduation Award, Tsinghua University \hfill{2006}

\item[] Undergraduate Student Fellowship, Tsinghua University \hfill{2003 - 2005}

\item[] 3rd Prize of Chinese National Chemistry Olympiad \hfill{2001}

\item[] 1st Prize of Chinese National Mathematics Olympiad \hfill{2001}

\end{list1}

% \section{\sc Teaching}
% \begin{list1}
% 
% \item[] Teaching Assistant: Introduction to Computer Science II, UC Irvine \hfill{Spring 2010}
% \item[] Teaching Assistant: Introduction to Computer Science I, UC Irvine \hfill{Fall 2009}
% \item[] Teaching Assistant: Introduction to Facility Planning, HKUST \hfill{Fall 2007}
% 
% \end{list1}

% Patents
% \section{\sc Patents}
% \begin{list1}
% 
% \item[] Frank Dellaert, Michael Kaess, {\bf Kai Ni}, ``Flow Separation for Stereo Visual Odometry''. \\
% Patent NO. US20110169923 A1. Assignee: GTRC.
% \vspace{2pt}
% 
% \item[] Hailin Jin, {\bf Kai Ni}, ``Region-Based Dense Feature Correspondence''. \\
% Patent NO. US8270770 B1. Assignee: Adobe Systems Inc.
% \vspace{2pt}
% 
% \item[] Hailin Jin, {\bf Kai Ni}, ``Random Sample Consensus for Groups of Data''. \\
% Patent NO. US20130124147 A1. Assignee: Adobe Systems Inc.
% \vspace{2pt}
% 
% \item[] Hailin Jin, {\bf Kai Ni}, ``Point Selection in Bundle Adjustment''. \\
% Patent No. US20130121558 A1. Assignee: Adobe Systems Inc.
% \vspace{2pt}
% 
% \end{list1}


\section{\sc Computer Skills}
\begin{list1}

\item[] Languages: Python, C, C++, Matlab, HTML, Java, Javascript.
\item[]	Tools: Linux Shell, Vim, PyTorch, Caffe, Tensorflow, Torch, OpenCV, Latex, GNU Make. 
% \item[] OS: Linux, Mac OS, Windows.

\end{list1}

\end{resume}
\end{document}
